### 2023-03-21 final_files/main.tex
done?

When behavioral protection is high, the effect of asymptomatic proportion on fatalities shows countervailing effects of individual-level protection and population-level risk (\fref{base}C).
For high values of $\delta$, the peak fatality occurs at intermediate levels of asymptomatic spread:
although fewer individuals die per infection for higher values of $p$, the increase in total infections still leads to an increase in total fatalities.
In contrast, when $\delta$ is small enough that $(1-\delta) \RR_s \geq \RR_a$ (in this case, $\delta < 0.25$), both the number of infections and the IFR ($(1-p)f$) decrease with increasing $p$.
We note that these results are robust to uncertainties in asymptomatic transmission rate.
In Supplementary Figure S2, we perform the same analysis while varying the ratio between $\RR_a$ and $\RR_s$ between 0.25 and 1.
In this case, qualitative predictions are robust when $\RR_a \geq 0.5 \RR_s$
--- when $\RR_a = 0.25 \RR_s$ and $\delta$ is large then $\RR_0 < 1$ and the epidemic does not take off.
In Supplementary Figure S3, we perform the same sensitivity analysis as Supplementary Figure S2 while fixing $\RR_0 = 4$ when $p=0.5$ and $\delta=0$ to prevent the epidemic from dying out. In this case, we find that intermediate values of asymptomaticity lead to the highest epidemic fatalities at high $\delta$ values across all ranges of $\RR_a/\RR_s$ we consider.

@@

\bibliography{main}

>>>>

When behavioral protection is high, the effect of asymptomatic proportion on fatalities shows countervailing effects of individual-level protection and population-level risk (\fref{base}C).
For high values of $\delta$, the peak fatality occurs at intermediate levels of asymptomatic spread:
although fewer individuals die per infection for higher values of $p$, the increase in total infections still leads to an increase in total fatalities.
In contrast, when $\delta$ is small enough that $(1-\delta) \RR_s \geq \RR_a$ (in this case, $\delta < 0.25$), both the number of infections and the IFR ($(1-p)f$) decrease with increasing $p$.
We note that these results are robust to uncertainties in asymptomatic transmission rate.
In Supplementary Figure S1, we perform the same analysis while varying the ratio between $\RR_a$ and $\RR_s$ between 0.25 and 1.
In this case, qualitative predictions are robust when $\RR_a \geq 0.5 \RR_s$
--- when $\RR_a = 0.25 \RR_s$ and $\delta$ is large then $\RR_0 < 1$ and the epidemic does not take off.
In Supplementary Figure S2, we perform the same sensitivity analysis as Supplementary Figure S1 while fixing $\RR_0 = 4$ when $p=0.5$ and $\delta=0$ to prevent the epidemic from dying out. In this case, we find that intermediate values of asymptomaticity lead to the highest epidemic fatalities at high $\delta$ values across all ranges of $\RR_a/\RR_s$ we consider.

@@

\begin{thebibliography}{10}

\bibitem{nogrady2020data}
Bianca Nogrady.
\newblock What the data say about asymptomatic {COVID} infections.
\newblock {\em Nature}, 587(7835):534--536, 2020.

\bibitem{rajgor2020many}
Dimple~D Rajgor, Meng~Har Lee, Sophia Archuleta, Natasha Bagdasarian, and
  Swee~Chye Quek.
\newblock {The many estimates of the COVID-19 case fatality rate}.
\newblock {\em The Lancet Infectious Diseases}, 20(7):776--777, 2020.

\bibitem{VERITY2020669}
Robert Verity, Lucy~C Okell, Ilaria Dorigatti, Peter Winskill, Charles
  Whittaker, Natsuko Imai, Gina Cuomo-Dannenburg, Hayley Thompson, Patrick G~T
  Walker, Han Fu, Amy Dighe, Jamie~T Griffin, Marc Baguelin, Sangeeta Bhatia,
  Adhiratha Boonyasiri, Anne Cori, Zulma Cucunubá, Rich FitzJohn, Katy
  Gaythorpe, Will Green, Arran Hamlet, Wes Hinsley, Daniel Laydon, Gemma
  Nedjati-Gilani, Steven Riley, Sabine {van Elsland}, Erik Volz, Haowei Wang,
  Yuanrong Wang, Xiaoyue Xi, Christl~A Donnelly, Azra~C Ghani, and Neil~M
  Ferguson.
\newblock Estimates of the severity of coronavirus disease 2019: a model-based
  analysis.
\newblock {\em The Lancet Infectious Diseases}, 20(6):669--677, 2020.

\bibitem{yang2020early}
Shu Yang, Peihua Cao, Peipei Du, Ziting Wu, Zian Zhuang, Lin Yang, Xuan Yu,
  Qi~Zhou, Xixi Feng, Xiaohui Wang, Weiguo Li, Enmei Liu, Ju~Chen, Yaolong
  Chen, and {Daihai He on behalf of COVID-19 evidence and recommendations
  working group}.
\newblock {Early estimation of the case fatality rate of COVID-19 in mainland
  China: a data-driven analysis}.
\newblock {\em Annals of translational medicine}, 8(4), 2020.

\bibitem{levin2020assessing}
Andrew~T Levin, William~P Hanage, Nana Owusu-Boaitey, Kensington~B Cochran,
  Seamus~P Walsh, and Gideon Meyerowitz-Katz.
\newblock {Assessing the age specificity of infection fatality rates for
  COVID-19: systematic review, meta-analysis, and public policy implications}.
\newblock {\em European journal of epidemiology}, 35(12):1123--1138, 2020.

\bibitem{emery2020}
Jon~C Emery, Timothy~W Russell, Yang Liu, Joel Hellewell, Carl~AB Pearson,
  CMMID COVID-19~Working Group, Gwenan~M Knight, Rosalind~M Eggo, Adam~J
  Kucharski, Sebastian Funk, Stefan Flasche, and Rein~MGJ Houben.
\newblock {The contribution of asymptomatic SARS-CoV-2 infections to
  transmission on the Diamond Princess cruise ship}.
\newblock {\em eLife}, 9:e58699, aug 2020.

\bibitem{ggplot2}
Hadley Wickham.
\newblock {\em {ggplot2: Elegant Graphics for Data Analysis}}.
\newblock Springer-Verlag New York, 2016.

\bibitem{Kissler2020}
Stephen~M. Kissler, Joseph~R. Fauver, Christina Mack, Scott~W. Olesen, Caroline
  Tai, Kristin~Y. Shiue, Chaney~C. Kalinich, Sarah Jednak, Isabel~M. Ott,
  Chantal~B.F. Vogels, Jay Wohlgemuth, James Weisberger, John DiFiori,
  Deverick~J. Anderson, Jimmie Mancell, David~D. Ho, Nathan~D. Grubaugh, and
  Yonatan~H. Grad.
\newblock {Viral dynamics of acute SARS-CoV-2 infection}.
\newblock {\em medRxiv}, 2021.

\bibitem{davies2020}
Nicholas~G. Davies, Petra Klepac, Yang Liu, Kiesha Prem, Mark Jit, Rosalind~M.
  Eggo, and {CMMID COVID-19 working group}.
\newblock {Age-dependent effects in the transmission and control of COVID-19
  epidemics}.
\newblock {\em Nature Medicine}, 26(8):1205--1211, 2020.

\bibitem{gao2021role}
Wenjing Gao, Jun Lv, Yuanjie Pang, and Li-Ming Li.
\newblock {Role of asymptomatic and pre-symptomatic infections in COVID-19
  pandemic}.
\newblock {\em bmj}, 375, 2021.

\bibitem{johansson2021sars}
Michael~A Johansson, Talia~M Quandelacy, Sarah Kada, Pragati~Venkata Prasad,
  Molly Steele, John~T Brooks, Rachel~B Slayton, Matthew Biggerstaff, and Jay~C
  Butler.
\newblock {SARS-CoV-2 transmission from people without COVID-19 symptoms}.
\newblock {\em JAMA network open}, 4(1):e2035057--e2035057, 2021.

\bibitem{subramanian2021quantifying}
Rahul Subramanian, Qixin He, and Mercedes Pascual.
\newblock {Quantifying asymptomatic infection and transmission of COVID-19 in
  New York City using observed cases, serology, and testing capacity}.
\newblock {\em Proceedings of the National Academy of Sciences},
  118(9):e2019716118, 2021.

\bibitem{koelle2022changing}
Katia Koelle, Michael~A Martin, Rustom Antia, Ben Lopman, and Natalie~E Dean.
\newblock {The changing epidemiology of SARS-CoV-2}.
\newblock {\em Science}, 375(6585):1116--1121, 2022.

\bibitem{lizewski2022navy}
Rhonda~A. Lizewski, Rachel S.~G. Sealfon, Sang~Woo Park, Gregory~R. Smith,
  Chad~K. Porter, Ana~S. Gonzalez-Reiche, Yongchao Ge, Clare~M. Miller, Carl~W.
  Goforth, Hanna Pincas, Michael~S. Termini, Irene Ramos, Venugopalan~D. Nair,
  Stephen~E. Lizewski, Hala Alshammary, Regina~Z. Cer, Hua~Wei Chen,
  Mary-Catherine George, Catherine~E. Arnold, Lindsay~A. Glang, Kyle~A. Long,
  Francisco Malagon, Jan~J. Marayag, Edgar Nunez, Gregory~K. Rice, Ernesto
  Santa~Ana, Megan~A. Schilling, Darci~R. Smith, Victor~A. Sugiharto, Peifang
  Sun, Adriana van~de Guchte, Zenab Khan, Jayeeta Dutta, Sindhu Vangeti,
  Logan~J. Voegtly, Dawn~L. Weir, C.~Jessica~E. Metcalf, Olga~G. Troyanskaya,
  Kimberly~A. Bishop-Lilly, Bryan~T. Grenfell, Harm van Bakel, Andrew~G.
  Letizia, and Stuart~C. Sealfon.
\newblock {SARS-CoV-2} outbreak dynamics in an isolated {US} military recruit
  training center with rigorous prevention measures.
\newblock {\em Epidemiology}, 33(6), 2022.

\bibitem{mizumoto2020estimating}
Kenji Mizumoto, Katsushi Kagaya, Alexander Zarebski, and Gerardo Chowell.
\newblock {Estimating the asymptomatic proportion of coronavirus disease 2019
  (COVID-19) cases on board the Diamond Princess cruise ship, Yokohama, Japan,
  2020}.
\newblock {\em Eurosurveillance}, 25(10):2000180, 2020.

\bibitem{ferretti2020quantifying}
Luca Ferretti, Chris Wymant, Michelle Kendall, Lele Zhao, Anel Nurtay, Lucie
  Abeler-D{\"o}rner, Michael Parker, David Bonsall, and Christophe Fraser.
\newblock {Quantifying SARS-CoV-2 transmission suggests epidemic control with
  digital contact tracing}.
\newblock {\em Science}, 368(6491):eabb6936, 2020.

\bibitem{lavezzo2020}
Enrico Lavezzo, Elisa Franchin, Constanze Ciavarella, Gina Cuomo-Dannenburg,
  Luisa Barzon, Claudia Del~Vecchio, Lucia Rossi, Riccardo Manganelli, Arianna
  Loregian, Nicol{\`o} Navarin, Davide Abate, Manuela Sciro, Stefano
  Merigliano, Ettore De~Canale, Maria~Cristina Vanuzzo, Valeria Besutti,
  Francesca Saluzzo, Francesco Onelia, Monia Pacenti, Saverio~G. Parisi,
  Giovanni Carretta, Daniele Donato, Luciano Flor, Silvia Cocchio, Giulia Masi,
  Alessandro Sperduti, Lorenzo Cattarino, Renato Salvador, Michele Nicoletti,
  Federico Caldart, Gioele Castelli, Eleonora Nieddu, Beatrice Labella,
  Ludovico Fava, Matteo Drigo, Katy A.~M. Gaythorpe, Alessandra~R. Brazzale,
  Stefano Toppo, Marta Trevisan, Vincenzo Baldo, Christl~A. Donnelly, Neil~M.
  Ferguson, Ilaria Dorigatti, Andrea Crisanti, Kylie E.~C. Ainslie, Marc
  Baguelin, Samir Bhatt, Adhiratha Boonyasiri, Olivia Boyd, Helen~L. Coupland,
  Zulma Cucunub{\'a}, Bimandra~A. Djafaara, Christl~A. Donnelly, Sabine~L. van
  Elsland, Rich FitzJohn, Seth Flaxman, Katy A.~M. Gaythorpe, Will~D. Green,
  Timothy Hallett, Arran Hamlet, David Haw, Natsuko Imai, Benjamin Jeffrey,
  Edward Knock, Daniel~J. Laydon, Thomas Mellan, Swapnil Mishra, Gemma
  Nedjati-Gilani, Pierre Nouvellet, Lucy~C. Okell, Kris~V. Parag, Steven Riley,
  Hayley~A. Thompson, H.~Juliette~T. Unwin, Robert Verity, Michaela A.~C.
  Vollmer, Patrick G.~T. Walker, Caroline~E. Walters, Haowei Wang, Yuanrong
  Wang, Oliver~J. Watson, Charles Whittaker, Lilith~K. Whittles, Xiaoyue Xi,
  Neil~M. Ferguson, and {Imperial College COVID-19 Response Team}.
\newblock {Suppression of a SARS-CoV-2 outbreak in the Italian municipality of
  Vo'}.
\newblock {\em Nature}, 584(7821):425--429, 2020.

\bibitem{romero2021ct}
Mar{\'\i}a~Pilar Romero-G{\'o}mez, Silvia G{\'o}mez-Sebastian, Emilio
  Cendejas-Bueno, Mar{\'\i}a~Dolores Montero-Vega, Jes{\'u}s Mingorance, and
  Julio Garc{\'\i}a-Rodr{\'\i}guez.
\newblock Ct value is not enough to discriminate patients harbouring infective
  virus.
\newblock {\em Journal of Infection}, 82(3):e35--e37, 2021.

\bibitem{stadnytskyi2021breathing}
V~Stadnytskyi, P~Anfinrud, and A~Bax.
\newblock {Breathing, speaking, coughing or sneezing: What drives transmission
  of SARS-CoV-2?}
\newblock {\em Journal of Internal Medicine}, 290(5):1010--1027, 2021.

\bibitem{alene2021magnitude}
Muluneh Alene, Leltework Yismaw, Moges~Agazhe Assemie, Daniel~Bekele Ketema,
  Belayneh Mengist, Bekalu Kassie, and Tilahun~Yemanu Birhan.
\newblock {Magnitude of asymptomatic COVID-19 cases throughout the course of
  infection: A systematic review and meta-analysis}.
\newblock {\em PloS one}, 16(3):e0249090, 2021.

\bibitem{fraser2004factors}
Christophe Fraser, Steven Riley, Roy~M Anderson, and Neil~M Ferguson.
\newblock Factors that make an infectious disease outbreak controllable.
\newblock {\em Proceedings of the National Academy of Sciences},
  101(16):6146--6151, 2004.

\bibitem{moghadas2020implications}
Seyed~M Moghadas, Meagan~C Fitzpatrick, Pratha Sah, Abhishek Pandey, Affan
  Shoukat, Burton~H Singer, and Alison~P Galvani.
\newblock {The implications of silent transmission for the control of COVID-19
  outbreaks}.
\newblock {\em Proceedings of the National Academy of Sciences},
  117(30):17513--17515, 2020.

\bibitem{xie2022long}
Yan Xie, Evan Xu, Benjamin Bowe, and Ziyad Al-Aly.
\newblock {Long-term cardiovascular outcomes of COVID-19}.
\newblock {\em Nature medicine}, 28(3):583--590, 2022.

\bibitem{he2020temporal}
Xi~He, Eric H.~Y. Lau, Peng Wu, Xilong Deng, Jian Wang, Xinxin Hao, Yiu~Chung
  Lau, Jessica~Y. Wong, Yujuan Guan, Xinghua Tan, Xiaoneng Mo, Yanqing Chen,
  Baolin Liao, Weilie Chen, Fengyu Hu, Qing Zhang, Mingqiu Zhong, Yanrong Wu,
  Lingzhai Zhao, Fuchun Zhang, Benjamin~J. Cowling, Fang Li, and Gabriel~M.
  Leung.
\newblock {Temporal dynamics in viral shedding and transmissibility of
  COVID-19}.
\newblock {\em Nature Medicine}, 26(5):672--675, 2020.

\bibitem{sender2021unmitigated}
Ron Sender, Yinon~M Bar-On, Sang~Woo Park, Elad Noor, Jonathan Dushoffd, and
  Ron Milo.
\newblock {The unmitigated profile of COVID-19 infectiousness}.
\newblock {\em medRxiv}, 2021.

\bibitem{kucharski2020effectiveness}
Adam~J Kucharski, Petra Klepac, Andrew~JK Conlan, Stephen~M Kissler, Maria~L
  Tang, Hannah Fry, Julia~R Gog, W~John Edmunds, and {CMMID COVID-19 working
  group}.
\newblock Effectiveness of isolation, testing, contact tracing, and physical
  distancing on reducing transmission of sars-cov-2 in different settings: a
  mathematical modelling study.
\newblock {\em The Lancet Infectious Diseases}, 20(10):1151--1160, 2020.

\bibitem{lipsitch2020understanding}
Marc Lipsitch and Natalie~E Dean.
\newblock Understanding {COVID-19} vaccine efficacy.
\newblock {\em Science}, 370(6518):763--765, 2020.

\bibitem{andres2022omicron}
Nick Andrews, Julia Stowe, Freja Kirsebom, Samuel Toffa, Tim Rickeard, Eileen
  Gallagher, Charlotte Gower, Meaghan Kall, Natalie Groves, Anne-Marie
  O’Connell, David Simons, Paula~B. Blomquist, Asad Zaidi, Sophie Nash, Nurin
  Iwani Binti Abdul~Aziz, Simon Thelwall, Gavin Dabrera, Richard Myers, Gayatri
  Amirthalingam, Saheer Gharbia, Jeffrey~C. Barrett, Richard Elson, Shamez~N.
  Ladhani, Neil Ferguson, Maria Zambon, Colin~N.J. Campbell, Kevin Brown, Susan
  Hopkins, Meera Chand, Mary Ramsay, and Jamie Lopez~Bernal.
\newblock Covid-19 vaccine effectiveness against the {Omicron (B.1.1.529)}
  variant.
\newblock {\em New England Journal of Medicine}, 386(16):1532--1546, 2022.

\bibitem{pearson2021omicron}
Carl A.~B. Pearson, Sheetal~P. Silal, Michael~W.Z. Li, Jonathan Dushoff,
  Benjamin~M. Bolker, Sam Abbott, Cari van Schalkwyk, Nicholas~G. Davies,
  Rosanna~C. Barnard, W.~John Edmunds, Jeremy Bingham, Gesine Meyer-Rath, Lise
  Jamieson, Allison Glass, Nicole Wolter, Nevashan Govender, Wendy~S. Stevens,
  Lesley Scott, Koleka Mlisana, Harry Moultrie, and Juliet R.~C. Pulliam.
\newblock {Bounding the levels of transmissibility \& immune evasion of the
  Omicron variant in South Africa}.
\newblock {\em medRxiv}, 2021.

\bibitem{sun2022omicron}
Kaiyuan Sun, Stefano Tempia, Jackie Kleynhans, Anne~von Gottberg, Meredith~L
  McMorrow, Nicole Wolter, Jinal~N. Bhiman, Jocelyn Moyes, Mignon~du Plessis,
  Maimuna Carrim, Amelia Buys, Neil~A Martinson, Kathleen Kahn, Stephen
  Tollman, Limakatso Lebina, Floidy Wafawanaka, Jacques~D. du~Toit,
  Francesc~Xavier G{\'o}mez-Oliv{\'e}, Thulisa Mkhencele, C{\'e}cile Viboud,
  Cheryl Cohen, and the PHIRST~group.
\newblock {Persistence of SARS-CoV-2 immunity, Omicron{\textquoteright}s
  footprints, and projections of epidemic resurgences in South African
  population cohorts}.
\newblock {\em medRxiv}, 2022.

\bibitem{MENNI20221618}
Cristina Menni, Ana~M Valdes, Lorenzo Polidori, Michela Antonelli, Satya
  Penamakuri, Ana Nogal, Panayiotis Louca, Anna May, Jane~C Figueiredo,
  Christina Hu, Erika Molteni, Liane Canas, Marc~F Österdahl, Marc Modat,
  Carole~H Sudre, Ben Fox, Alexander Hammers, Jonathan Wolf, Joan Capdevila,
  Andrew~T Chan, Sean~P David, Claire~J Steves, Sebastien Ourselin, and Tim~D
  Spector.
\newblock {Symptom prevalence, duration, and risk of hospital admission in
  individuals infected with SARS-CoV-2 during periods of omicron and delta
  variant dominance: a prospective observational study from the ZOE COVID
  Study}.
\newblock {\em The Lancet}, 399(10335):1618--1624, 2022.

\bibitem{ulloa2022estimates}
Ana~Cecilia Ulloa, Sarah~A Buchan, Nick Daneman, and Kevin~A Brown.
\newblock {Estimates of SARS-CoV-2 omicron variant severity in Ontario,
  Canada}.
\newblock {\em Jama}, 327(13):1286--1288, 2022.

\bibitem{Iacobuccio254}
Gareth Iacobucci.
\newblock Covid-19: unravelling the conundrum of {Omicron} and deaths.
\newblock {\em BMJ}, 376, 2022.

\bibitem{faust2022omicron}
Jeremy~Samuel Faust, Chengan Du, Chenxue Liang, Katherine~Dickerson Mayes,
  Benjamin Renton, Kristen Panthagani, and Harlan~M. Krumholz.
\newblock {Excess Mortality in {Massachusetts} During the {Delta} and {Omicron}
  Waves of {COVID-19}}.
\newblock {\em JAMA}, 05 2022.

\bibitem{sigal2022estimating}
Alex Sigal, Ron Milo, and Waasila Jassat.
\newblock {Estimating disease severity of Omicron and Delta SARS-CoV-2
  infections}.
\newblock {\em Nature Reviews Immunology}, pages 1--3, 2022.

\bibitem{saad2020immune}
Chadi~M Saad-Roy, Caroline~E Wagner, Rachel~E Baker, Sinead~E Morris, Jeremy
  Farrar, Andrea~L Graham, Simon~A Levin, Michael~J Mina, C~Jessica~E Metcalf,
  and Bryan~T Grenfell.
\newblock {Immune life history, vaccination, and the dynamics of SARS-CoV-2
  over the next 5 years}.
\newblock {\em Science}, 370(6518):811--818, 2020.

\bibitem{gallagher2021indirect}
Molly~E Gallagher, Andrew~J Sieben, Kristin~N Nelson, Alicia~NM Kraay, Walter~A
  Orenstein, Ben Lopman, Andreas Handel, and Katia Koelle.
\newblock {Indirect benefits are a crucial consideration when evaluating
  SARS-CoV-2 vaccine candidates}.
\newblock {\em Nature medicine}, 27(1):4--5, 2021.

\bibitem{park2020time}
Sang~Woo Park, Daniel~M Cornforth, Jonathan Dushoff, and Joshua~S Weitz.
\newblock {The time scale of asymptomatic transmission affects estimates of
  epidemic potential in the COVID-19 outbreak}.
\newblock {\em Epidemics}, 31:100392, 2020.

\bibitem{harris2023time}
Jeremy~D Harris, Sang~Woo Park, Jonathan Dushoff, and Joshua~S Weitz.
\newblock How time-scale differences in asymptomatic and symptomatic
  transmission shape sars-cov-2 outbreak dynamics.
\newblock {\em Epidemics}, page 100664, 2023.

\bibitem{moore2021modelling}
Sam Moore, Edward~M Hill, Louise Dyson, Michael~J Tildesley, and Matt~J
  Keeling.
\newblock {Modelling optimal vaccination strategy for SARS-CoV-2 in the UK}.
\newblock {\em PLoS computational biology}, 17(5):e1008849, 2021.

\bibitem{weitz2020awareness}
Joshua~S Weitz, Sang~Woo Park, Ceyhun Eksin, and Jonathan Dushoff.
\newblock Awareness-driven behavior changes can shift the shape of epidemics
  away from peaks and toward plateaus, shoulders, and oscillations.
\newblock {\em Proceedings of the National Academy of Sciences},
  117(51):32764--32771, 2020.

\bibitem{kissler2020projecting}
Stephen~M Kissler, Christine Tedijanto, Edward Goldstein, Yonatan~H Grad, and
  Marc Lipsitch.
\newblock {Projecting the transmission dynamics of SARS-CoV-2 through the
  postpandemic period}.
\newblock {\em Science}, 368(6493):860--868, 2020.

\bibitem{lavine2021immunological}
Jennie~S Lavine, Ottar~N Bjornstad, and Rustom Antia.
\newblock {Immunological characteristics govern the transition of COVID-19 to
  endemicity}.
\newblock {\em Science}, 371(6530):741--745, 2021.

\bibitem{gandon2001imperfect}
Sylvain Gandon, Margaret~J Mackinnon, Sean Nee, and Andrew~F Read.
\newblock Imperfect vaccines and the evolution of pathogen virulence.
\newblock {\em Nature}, 414(6865):751--756, 2001.

\bibitem{Bavel2020}
Jay J.~Van Bavel, Katherine Baicker, Paulo~S. Boggio, Valerio Capraro,
  Aleksandra Cichocka, Mina Cikara, Molly~J. Crockett, Alia~J. Crum, Karen~M.
  Douglas, James~N. Druckman, John Drury, Oeindrila Dube, Naomi Ellemers,
  Eli~J. Finkel, James~H. Fowler, Michele Gelfand, Shihui Han, S.~Alexander
  Haslam, Jolanda Jetten, Shinobu Kitayama, Dean Mobbs, Lucy~E. Napper,
  Dominic~J. Packer, Gordon Pennycook, Ellen Peters, Richard~E. Petty, David~G.
  Rand, Stephen~D. Reicher, Simone Schnall, Azim Shariff, Linda~J. Skitka,
  Sandra~Susan Smith, Cass~R. Sunstein, Nassim Tabri, Joshua~A. Tucker, Sander
  van~der Linden, Paul~van Lange, Kim~A. Weeden, Michael J.~A. Wohl, Jamil
  Zaki, Sean~R. Zion, and Robb Willer.
\newblock {Using social and behavioural science to support COVID-19 pandemic
  response}.
\newblock {\em Nature Human Behaviour}, 4(5):460--471, 2020.

\bibitem{chande2020real}
Aroon Chande, Seolha Lee, Mallory Harris, Quan Nguyen, Stephen~J Beckett, Troy
  Hilley, Clio Andris, and Joshua~S Weitz.
\newblock {Real-time, interactive website for US-county-level COVID-19 event
  risk assessment}.
\newblock {\em Nature Human Behaviour}, 4(12):1313--1319, 2020.

\bibitem{sinclair2021pairing}
Alyssa~H Sinclair, Shabnam Hakimi, Matthew~L Stanley, R~Alison Adcock, and
  Gregory~R Samanez-Larkin.
\newblock Pairing facts with imagined consequences improves pandemic-related
  risk perception.
\newblock {\em Proceedings of the National Academy of Sciences},
  118(32):e2100970118, 2021.

\bibitem{mina2021covid}
Michael~J Mina and Kristian~G Andersen.
\newblock {COVID-19} testing: One size does not fit all.
\newblock {\em Science}, 371(6525):126--127, 2021.

\bibitem{gibson2022surv}
Greg Gibson, Joshua~S. Weitz, Michael~P. Shannon, Benjamin Holton, Anton
  Bryksin, Brian Liu, Madeline Sieglinger, Ashley~R. Coenen, Conan Zhao,
  Stephen~J. Beckett, Sandra Bramblett, JulieAnne Williamson, Michael Farrell,
  Alexander Ortiz, Chaouki~T. Abdallah, and Andr{\'e}s~J. Garc{\'\i}a.
\newblock Surveillance-to-diagnostic testing program for asymptomatic
  {SARS-CoV-2} infections on a large, urban campus in fall 2020.
\newblock {\em Epidemiology}, 33(2), 2022.

\bibitem{Ranoa2022}
Diana Rose~E. Ranoa, Robin~L. Holland, Fadi~G. Alnaji, Kelsie~J. Green, Leyi
  Wang, Richard~L. Fredrickson, Tong Wang, George~N. Wong, Johnny Uelmen,
  Sergei Maslov, Zachary~J. Weiner, Alexei~V. Tkachenko, Hantao Zhang, Zhiru
  Liu, Ahmed Ibrahim, Sanjay~J. Patel, John~M. Paul, Nickolas~P. Vance,
  Joseph~G. Gulick, Sandeep~Puthanveetil Satheesan, Isaac~J. Galvan, Andrew
  Miller, Joseph Grohens, Todd~J. Nelson, Mary~P. Stevens, P.~Mark Hennessy,
  Robert~C. Parker, Edward Santos, Charles Brackett, Julie~D. Steinman,
  Melvin~R. Fenner, Kirstin Dohrer, Michael DeLorenzo, Laura Wilhelm-Barr,
  Brian~R. Brauer, Catherine Best-Popescu, Gary Durack, Nathan Wetter, David~M.
  Kranz, Jessica Breitbarth, Charlie Simpson, Julie~A. Pryde, Robin~N. Kaler,
  Chris Harris, Allison~C. Vance, Jodi~L. Silotto, Mark Johnson, Enrique~Andres
  Valera, Patricia~K. Anton, Lowa Mwilambwe, Stephen~P. Bryan, Deborah~S.
  Stone, Danita~B. Young, Wanda~E. Ward, John Lantz, John~A. Vozenilek, Rashid
  Bashir, Jeffrey~S. Moore, Mayank Garg, Julian~C. Cooper, Gillian Snyder,
  Michelle~H. Lore, Dustin~L. Yocum, Neal~J. Cohen, Jan~E. Novakofski,
  Melanie~J. Loots, Randy~L. Ballard, Mark Band, Kayla~M. Banks, Joseph~D.
  Barnes, Iuliana Bentea, Jessica Black, Jeremy Busch, Abigail Conte, Madison
  Conte, Michael Curry, Jennifer Eardley, April Edwards, Therese Eggett, Judes
  Fleurimont, Delaney Foster, Bruce~W. Fouke, Nicholas Gallagher, Nicole
  Gastala, Scott~A. Genung, Declan Glueck, Brittani Gray, Andrew Greta,
  Robert~M. Healy, Ashley Hetrick, Arianna~A. Holterman, Nahed Ismail, Ian
  Jasenof, Patrick Kelly, Aaron Kielbasa, Teresa Kiesel, Lorenzo~M. Kindle,
  Rhonda~L. Lipking, Yukari~C. Manabe, Jade Mayes, Reubin McGuffin, Kenton~G.
  McHenry, Agha Mirza, Jada Moseley, Heba~H. Mostafa, Melody Mumford, Kathleen
  Munoz, Arika~D. Murray, Moira Nolan, Nil~A. Parikh, Andrew Pekosz, Janna
  Pflugmacher, Janise~M. Phillips, Collin Pitts, Mark~C. Potter, James
  Quisenberry, Janelle Rear, Matthew~L. Robinson, Edith Rosillo, Leslie~N. Rye,
  MaryEllen Sherwood, Anna Simon, Jamie~M. Singson, Carly Skadden, Tina~H.
  Skelton, Charlie Smith, Mary Stech, Ryan Thomas, Matthew~A. Tomaszewski,
  Erika~A. Tyburski, Scott Vanwingerden, Evette Vlach, Ronald~S. Watkins,
  Karriem Watson, Karen~C. White, Timothy~L. Killeen, Robert~J. Jones,
  Andreas~C. Cangellaris, Susan~A. Martinis, Awais Vaid, Christopher~B. Brooke,
  Joseph~T. Walsh, Ahmed Elbanna, William~C. Sullivan, Rebecca~L. Smith, Nigel
  Goldenfeld, Timothy~M. Fan, Paul~J. Hergenrother, and Martin~D. Burke.
\newblock {Mitigation of SARS-CoV-2 transmission at a large public university}.
\newblock {\em Nature Communications}, 13(1):3207, 2022.

\bibitem{jones2020two}
Nicholas~R Jones, Zeshan~U Qureshi, Robert~J Temple, Jessica~PJ Larwood, Trisha
  Greenhalgh, and Lydia Bourouiba.
\newblock Two metres or one: what is the evidence for physical distancing in
  {COVID-19?}
\newblock {\em bmj}, 370, 2020.

\bibitem{prather2020reducing}
Kimberly~A Prather, Chia~C Wang, and Robert~T Schooley.
\newblock Reducing transmission of {SARS-CoV-2}.
\newblock {\em Science}, 368(6498):1422--1424, 2020.

\bibitem{howard2021ev}
Jeremy Howard, Austin Huang, Zhiyuan Li, Zeynep Tufekci, Vladimir Zdimal,
  Helene-Mari van~der Westhuizen, Arne von Delft, Amy Price, Lex Fridman,
  Lei-Han Tang, Viola Tang, Gregory~L. Watson, Christina~E. Bax, Reshama
  Shaikh, Frederik Questier, Danny Hernandez, Larry~F. Chu, Christina~M.
  Ramirez, and Anne~W. Rimoin.
\newblock {An evidence review of face masks against COVID-19}.
\newblock {\em Proceedings of the National Academy of Sciences},
  118(4):e2014564118, 2021.

\bibitem{allen2021indoor}
Joseph~G Allen and Andrew~M Ibrahim.
\newblock {Indoor air changes and potential implications for SARS-CoV-2
  transmission}.
\newblock {\em Jama}, 325(20):2112--2113, 2021.

\bibitem{wang2021airborne}
Chia~C Wang, Kimberly~A Prather, Josu{\'e} Sznitman, Jose~L Jimenez, Seema~S
  Lakdawala, Zeynep Tufekci, and Linsey~C Marr.
\newblock Airborne transmission of respiratory viruses.
\newblock {\em Science}, 373(6558):eabd9149, 2021.

\bibitem{lopman2021framework}
Benjamin~A Lopman, Kayoko Shioda, Quan Nguyen, Stephen~J Beckett, Aaron~J
  Siegler, Patrick~S Sullivan, and Joshua~S Weitz.
\newblock {A framework for monitoring population immunity to SARS-CoV-2}.
\newblock {\em Annals of Epidemiology}, 63:75--78, 2021.

\bibitem{fox2020impact}
Spencer~J Fox, Remy Pasco, Mauricio Tec, Zhanwei Du, Michael Lachmann, James
  Scott, and Lauren~Ancel Meyers.
\newblock {The impact of asymptomatic COVID-19 infections on future pandemic
  waves}.
\newblock {\em MedRxiv}, pages 2020--06, 2020.

\bibitem{park2020reconciling}
Sang~Woo Park, Benjamin~M Bolker, David Champredon, David~JD Earn, Michael Li,
  Joshua~S Weitz, Bryan~T Grenfell, and Jonathan Dushoff.
\newblock {Reconciling early-outbreak estimates of the basic reproductive
  number and its uncertainty: framework and applications to the novel
  coronavirus (SARS-CoV-2) outbreak}.
\newblock {\em Journal of the Royal Society Interface}, 17(168):20200144, 2020.

\bibitem{smith1984assessment}
PG~Smith, LC~Rodrigues, and PEM Fine.
\newblock Assessment of the protective efficacy of vaccines against common
  diseases using case-control and cohort studies.
\newblock {\em International journal of epidemiology}, 13(1):87--93, 1984.

\bibitem{buckner2021dynamic}
Jack~H Buckner, Gerardo Chowell, and Michael~R Springborn.
\newblock {Dynamic prioritization of COVID-19 vaccines when social distancing
  is limited for essential workers}.
\newblock {\em Proceedings of the National Academy of Sciences},
  118(16):e2025786118, 2021.

\bibitem{bubar2021model}
Kate~M Bubar, Kyle Reinholt, Stephen~M Kissler, Marc Lipsitch, Sarah Cobey,
  Yonatan~H Grad, and Daniel~B Larremore.
\newblock {Model-informed COVID-19 vaccine prioritization strategies by age and
  serostatus}.
\newblock {\em Science}, 371(6532):916--921, 2021.

\end{thebibliography}
